Evaluate residuals in each cohort and brain region

### 2020-11-18 combined_analysis/eval_resid_in_each.Rmd
Initial commit

---
title: "Run PEER in each dataset"
subtitle: ''
author: "Developed by [Gabriel Hoffman](http://gabrielhoffman.github.io/)"
date: "Run on `r Sys.time()`"
documentclass: article
output: 
  html_document:
  toc: true
  smart: false
---

@@

cd /hpc/users/hoffmg01/work/covarr-de
# rm -rf molec_profiling_cache/
ml git pandoc
git pull
R

@@

rmarkdown::render("combined_analysis/peer_in_each.Rmd")

@@

```{r knit2synapse, eval=FALSE}
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "combined_analysis/peer_in_each.Rmd",
                                          parentId ="syn22012942",
                                          folderName = 'Run PEER in each dataset',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```

@@

library(githubr)
parentId = 'syn22012942';
activityName = 'Run PEER in each dataset';
activityDescription = 'Run PEER in each dataset';

thisFileName <- 'peer_in_each.Rmd'

@@

```{r}
CODE <- Folder(name = "Run PEER in each dataset", parentId = "syn22012942")
CODE <- synStore(CODE)

@@

form.lst = list(
  `MSSM-Penn-Pitt`  = ~ Dx + Reported_Gender + RIN +scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + Institution*(ageOfDeath + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3),
  `NIMH-HBCC`       = ~ Dx + Reported_Gender + RIN + scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + ageOfDeath + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3)

@@

@@

  # Compute residuals, but add back in Dx*Reported_Gender
  # for form = ~ Dx*Reported_Gender
  f = function(fit){
    residuals(fit) + get_prediction( fit, ~ Dx + Reported_Gender + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3)
  }

@@

>>>>

---
title: "Evaluate residuals in each cohort and brain region"
subtitle: ''
author: "Developed by [Gabriel Hoffman](http://gabrielhoffman.github.io/)"
date: "Run on `r Sys.time()`"
documentclass: article
output: 
  html_document:
  toc: true
  smart: false
---

@@

cd /hpc/users/hoffmg01/work/covarr-de
# rm -rf molec_profiling_cache/
ml git pandoc R/3.6.3 # to get peer
git pull
R

@@

rmarkdown::render("combined_analysis/eval_resid_in_each.Rmd")

@@

```{r knit2synapse, eval=FALSE}
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "combined_analysis/eval_resid_in_each.Rmd",
                                          parentId ="syn22012942",
                                          folderName = 'Evaluate residuals in each cohort and brain region',
                                          overwrite=TRUE, 
                                          knitmd=TRUE)
```

@@

library(githubr)
parentId = 'syn22012942';
activityName = 'Evaluate residuals in each cohort and brain region';
activityDescription = 'Evaluate residuals in each cohort and brain region';

thisFileName <- 'eval_resid_in_each.Rmd'

@@

```{r}
CODE <- Folder(name = "Evaluate residuals in each cohort and brain region", parentId = "syn22012942")
CODE <- synStore(CODE)

@@

# formula used to fit model
form.lst = list(
  `MSSM-Penn-Pitt`  = ~ Dx + Reported_Gender + RIN +scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + Institution*(ageOfDeath + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3),
  `NIMH-HBCC`       = ~ Dx + Reported_Gender + RIN + scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + ageOfDeath + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3)

asdfas

@@

  # add these terms back into the model
  form_add = ifelse(names(j) == "MSSM-Penn-Pitt",
        ~ Dx + Reported_Gender + Institution*(cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3),
        ~ Dx + Reported_Gender + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3)

@@

  # Compute residuals, but add back in Dx*Reported_Gender
  # for form = ~ Dx*Reported_Gender
  f = function(fit){
    residuals(fit) + get_prediction( fit, form_add)
  }

@@

```{r run.peer}

  model = PEER()

  PEER_setPhenoMean(model,as.matrix(expr))

  PEER_setCovariates(model, as.matrix(covs))

  PEER_setNk(model,10)

  PEER_update(model)

  latentVariables = PEER_getX(model)

```
